Using vector space models based on LDA and LSA for automatically grading exam questions

### 2018-06-15 tex/article.tex
Improved figure placement, referred to figures through refs, and removed number from Appendix heading.

\subsection{Best-performing individual models}
As explained in section \ref{sec:averageoutcomes}, all cells in Table \ref{table1} represent average outcomes.

The best-performing LDA model achieved a correlation of $\textit{r}_s$ = .52. It was trained on the textbook chapter, used binary counting, was spelling-corrected and used the x10 mapping algorithm. The scatterplot of predicted and assigned grades is shown in Figure 2.

\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{"Best LDA model"}
\caption{Grades predicted by the best LDA model.}
\label{lda}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{"Best LSA model"}
	\caption{Grades predicted by the best LSA model.}
	\label{lsa}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{"Best baseline model"}
	\caption{Grades predicted by the best baseline model.}
	\label{baseline}
\end{figure}

The best-performing LSA model achieved a correlation of $\textit{r}_s$ = .42. It was trained on non-spelling-corrected student answers and used binary counting. The mapping algorithm was not relevant, as no 1s and 9s were predicted to begin with. Figure 3 shows the scatterplot for this model.

Both of these models outperformed the best baseline model, which achieved a correlation of $\textit{r}_s$ = .38, using raw counts and spelling-corrected data. As in the LSA model, the mapping algorithm was irrelevant. The scatterplot is shown in Figure 4.

@@

\section{Appendix}
\begin{table}[]

>>>>

\subsection{Best-performing individual models}
As explained in Section \ref{sec:averageoutcomes}, all cells in Table \ref{table1} represent average outcomes.

The best-performing LDA model achieved a correlation of $\textit{r}_s$ = .52. It was trained on the textbook chapter, used binary counting, was spelling-corrected and used the x10 mapping algorithm. The scatterplot of predicted and assigned grades is shown in Figure \ref{lda}.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{"Best LDA model"}
\caption{Grades predicted by the best LDA model.}
\label{lda}
\end{figure}

The best-performing LSA model achieved a correlation of $\textit{r}_s$ = .42. It was trained on non-spelling-corrected student answers and used binary counting. The mapping algorithm was not relevant, as no 1s and 9s were predicted to begin with. Figure \ref{lsa} shows the scatterplot for this model.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{"Best LSA model"}
\caption{Grades predicted by the best LSA model.}
\label{lsa}
\end{figure}

Both of these models outperformed the best baseline model, which achieved a correlation of $\textit{r}_s$ = .38, using raw counts and spelling-corrected data. As in the LSA model, the mapping algorithm was irrelevant. The scatterplot is shown in Figure \ref{baseline}.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{"Best baseline model"}
\caption{Grades predicted by the best baseline model.}
\label{baseline}
\end{figure}

@@

\section*{Appendix}
\begin{table}[h]
